Low prevalence of \emph{a priori} power analyses in motor behavior research

### 2022-09-28 docs/submission/submission.Rmd
update: include link to github repo
update: fix behaviour spelling in github links
update: "blind" elements for journal requirement

Our design and analysis plan was preregistered after piloting our methods on a subsample of 40 papers. The preregistration, materials, data, and code from this study is available here: https://osf.io/wsdpv/.

@@

\noindent All authors thank Aaron Schwarz and Abigail Morgan for their help with data extraction.

## Open Science Practices
\noindent The preregistration, data, and scripts can be accessed here: https://osf.io/wsdpv/.

@@

\noindent This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University (MJC).

>>>>

Our design and analysis plan was preregistered after piloting our methods on a subsample of 40 papers. The preregistration, data, and code for this study is available using either of the following links: https://osf.io/wsdpv/ \censor{or} \censor{$https://github.com/cartermaclab/proj_power-motor-behaviour$}.

@@

\noindent All authors thank \censor{Aaron Schwarz} and \censor{Abigail Morgan} for their help with data extraction.

## Open Science Practices
\noindent The preregistration, data, and scripts can be accessed using either of the following links: https://osf.io/wsdpv/ \censor{or} \censor{$https://github.com/cartermaclab/proj_power-motor-behaviour$}.

@@

\noindent This work was supported by \blackout{the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University (MJC)}.

### 2022-09-28 docs/submission/submission.tex
update: include link to github repo
update: fix behaviour spelling in github links
update: "blind" elements for journal requirement

Our design and analysis plan was preregistered after piloting our methods on a subsample of 40 papers. The preregistration, materials, data, and code from this study is available here: \url{https://osf.io/wsdpv/}.

@@

\noindent All authors thank Aaron Schwarz and Abigail Morgan for their help with data extraction.

@@

\noindent The preregistration, data, and scripts can be accessed here: \url{https://osf.io/wsdpv/}.

>>>>

Our design and analysis plan was preregistered after piloting our methods on a subsample of 40 papers. The preregistration, data, and code for this study is available using either of the following links: \url{https://osf.io/wsdpv/} \censor{or} \censor{$https://github.com/cartermaclab/proj_power-motor-behaviour$}.

@@

\noindent All authors thank \censor{Aaron Schwarz} and \censor{Abigail Morgan} for their help with data extraction.

@@

\noindent The preregistration, data, and scripts can be accessed using either of the following links: \url{https://osf.io/wsdpv/} \censor{or} \censor{$https://github.com/cartermaclab/proj_power-motor-behaviour$}.
